Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-06-22 presentation/presentation.tex
[minor] add supplement ppt

\begin{frame}[noframenumbering]{Outline}
	\tableofcontents
\end{frame}

@@

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
					\item[\color{red}{$\times$}] Highly depends on simulated contour information.
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

		\begin{column}{0.5\textwidth}
			Tamei \textit{et al.}\footnotemark, ~Clothing assistance with dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Reinforcement
					      learning (RL)
					\item[\color{green}{\checkmark}] Topology coordinates for human and cloth extremities relationship
					\item[\color{red}{$\times$}] Limited generalization capability for new postures
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{tamei_2011}
			}
		\end{column}
	\end{columns}

@@

\section{Dynamic Movement Primitives}
\begin{frame}{Dynamic Movement Primitives (DMP)}
	%\linespread{1.2}

	\begin{exampleblock}{DMP in a nutshell}
		\begin{itemize}
			\item It is used for generating a control signal to guide the real system\footnotemark
			\item It can represent \textit{nonlinear} motion with a set of differential equations
		\end{itemize}
	\end{exampleblock}

	%	We start with point attractor dynamics\footcite{ijspeert2002movement} \hskip1em $\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})$

	%	\vskip -1em
	%	\begin{equation}
	%		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})
	%		\label{eq:attractor}
	%	\end{equation}
	%	\vskip -0.5em

	%	\vskip 1em
	%	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
	The system is defined as
	\vskip -1em
	\begin{equation}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation}
	%\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep-0.2em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}

	\begin{exampleblock}{}
		$f$ is a function of \textit{canonical system}, denoted by $x$ as $\dot{x} = -\alpha_x x$
	\end{exampleblock}

	\footcitetext{schaal2006dynamic}
\end{frame}

\begin{frame}{Forcing function $f$}
	$f$ is defined as
	\begin{equation}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation}

	where:
	\begin{itemize}
		\item $y_0$ is the initial state of the system
		\item $w_i$ is a weighting for a given basis function $\psi_i$
		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
	\end{itemize}

	\vskip -1em
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2.1cm]{psi_activation}
				\vskip -0.3em
				\caption{$\psi$ Activation}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2.1cm]{weighted_summation}
				\vskip -0.3em
				\caption{Weighted Summation}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Imitating a desired path}
	\linespread{1.4}
	The desired forcing term $f$ which affects the system acceleration, is written as
	\vskip -1.5em
	\begin{equation}
		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
		\label{eq:imitate_f}
	\end{equation}
	\vskip -0.5em
	{\small
		where 
		\vskip -1em
		\begin{itemize}
			\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
		\end{itemize}
	}
	\vskip-0.5em
	\begin{exampleblock}{}
		Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip-2em
		\begin{equation}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation}
	\end{exampleblock}
	\vskip-0.5em
	\begin{figure}
		\includegraphics[width=0.8\textwidth]{imitate_path}
	\end{figure}
	\vskip-1.5em
	\footcitetext{schaal2002scalable}
\end{frame}

@@

\section{Results}
\begin{frame}{Results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{trajectory}
				\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip 1em
	\centering{
		\href{run:./videos/video.mp4}{\beamerbutton{Video demonstration}}
	}
\end{frame}

\section{Conclusion and Discussion}
\begin{frame}{Conclusion and Discussion}
	\linespread{1.5}

	\begin{itemize}
		\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
		\item Result shows that DMPs are able to generalize the movement trajectory
		\item Proposed failure detection method by using force information can detect failures
		\item DMP should incorporate orientation information as well
	\end{itemize}
\end{frame}

@@

\begin{frame}[noframenumbering]{The End}
	\begin{center}
		\Huge Thanks for your attention!
		\vskip 1em \huge Any questions?
		\vskip 2em \normalsize \url{www.ravijoshi.xyz}
	\end{center}
\end{frame}

\end{document}

>>>>

\begin{frame}[noframenumbering,label=main]{Outline}
	\tableofcontents
\end{frame}

@@

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item Used Hidden Markov Model for tracking
					\item Triangulated mesh model for simulating clothing article
					\item Highly depends on simulated contour information.
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

		\begin{column}{0.5\textwidth}
			Tamei \textit{et al.}\footnotemark, ~Clothing assistance with dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item Used Reinforcement learning (RL)
					\item Topology coordinates for human and cloth extremities relationship
					\item Via-point trajectory with minimum jerk criterion
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{tamei_2011}
			}
		\end{column}
	\end{columns}

@@

\section{Dynamic Movement Primitives}
\begin{frame}{Dynamic Movement Primitives (DMP)}
	%\linespread{0.8}
	Used for generating control signal to guide real system\footnotemark
	\begin{exampleblock}{Why DMP?}
		\begin{itemize}
			\item A \textit{non-linear} dynamical system used for policy parameterization
			\item Can adapt to complex motor-skills
			\item Also perform target tracking and obstacle avoidance
		\end{itemize}
	\end{exampleblock}

	The system is defined as
	\vskip -1em
	\begin{equation*}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation*}
	\vskip -0.5em
	{\small
		where:
		\vskip -0.6em
		\begin{itemize}
			\itemsep0.1em
			\item $y$ is system state and $g$ is goal state
			\item $\alpha$ and $\beta$ are gain terms
			\item $f$ is nonlinear function defined over time
		\end{itemize}
	}
	\vskip -0.6em
	\begin{exampleblock}{}
		$f$ is a function of \textit{canonical system}, denoted by $x$ as $\dot{x} = -\alpha_x x$
	\end{exampleblock}

	\vskip -0.6em
	\footcitetext{schaal2006dynamic}
\end{frame}

\begin{frame}{Forcing function $f$}
	$f$ is defined as
	\vskip-2.8em
	\begin{equation*}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation*}
	\vskip-0.5em
	{\small
		where:
		%\vskip-0.8em
		\begin{itemize}
			\setlength\itemsep{0.2em}
			\item $y_0$ is the initial state of the system
			\item $w_i$ is a weighting for a given basis function $\psi_i$
			\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
		\end{itemize}
	}
	\vskip-1em
	\begin{exampleblock}{Imitating a desired path}
		The desired forcing term $f$ which affects the system acceleration, is written as
		\vskip-1em
		\begin{equation*}
			\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
			\label{eq:imitate_f}
		\end{equation*}

		Choose the weights over the basis functions i.e., minimize\footnotemark
		\vskip-1em
		\begin{equation*}
			\Sigma_t \psi_i(t) \left[ f_d(t) - w_i \left\lbrace x(t) (g - y_0)\right\rbrace\right]^2
			\label{eq:minize_fd}
		\end{equation*}
	\end{exampleblock}
	\vskip-1.5em
	\footcitetext{schaal2002scalable}
\end{frame}

@@

\section{Experiments and Results}
\begin{frame}{Experiments and Results}
	\begin{columns}[b]
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[trim={4cm 0 5cm 0},clip,width=\textwidth]{various_posture}
				\caption{Old \& modified posture of mannequin}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{all_traj}
				\caption{Left arm trajectories of Baxter Robot}
			\end{figure}
		\end{column}
	\end{columns}

	\vskip 1em
	\centering{
		\href{run:./videos/video.mp4}{\beamerbutton{Video Demonstration}}
	}
\end{frame}

\begin{frame}{Accuracy measurement}
	Angle of Inclination measures the bending of arms w.r.t. horizontal line in two-dimensional space
	\begin{columns}[t]
		\begin{column}{0.4\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{inclination_plus}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{success_rate}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\section{Discussion and Conclusion}
\begin{frame}{Discussion and Conclusion}
	\linespread{1.5}

	\begin{itemize}
		\item Robotic clothing assistance is challenging since it requires cooperative manipulation
		\item Clothing article inherits non-rigid and highly deformable properties
		\item Result shows that DMPs are able to generalize the movement trajectory
		\item DMP should incorporate orientation information as well
	\end{itemize}
\end{frame}

@@

\begin{frame}[noframenumbering]{The End}
	\begin{center}
		\Huge Thanks for your attention!
		\vskip 1em \huge Any questions?
		\vskip 2em \normalsize \url{www.ravijoshi.xyz}
	\end{center}
	\centering{\hyperlink{supplemental}{\beamerbutton{supplemental here}}}
\end{frame}

\appendix
\section{More}
\begin{frame}[noframenumbering,label=supplemental]
	\frametitle{Dynamic Movement Primitives (DMP)}
	\linespread{1.2}

	\begin{exampleblock}{DMP in a nutshell}
		\begin{itemize}
			\item A method of trajectory control/planning\footnotemark
			\item Complex movements are considered as composed of sets of primitive action ‘building blocks’
			      \begin{itemize}
			      	\item Executed in sequence \textit{and/or} in parallel
			      	\item DMPs are a proposed mathematical formalization of these primitives.
			      \end{itemize}
			\item It can represent \textit{nonlinear} motion with a set of differential equations
			\item These equations can be adapted to generate any movement trajectory
		\end{itemize}
	\end{exampleblock}

	\footnotetext{\tiny Schaal, Stefan. ``Dynamic movement primitives-a framework for motor control in humans and humanoid robotics." Adaptive Motion of Animals and Machines.  Springer Tokyo, 2006. 261-280.}
\end{frame}

\begin{frame}[noframenumbering]{Formulation of DMP}
	\linespread{1.2}

	\textit{DMP is for generating a control signal to guide the real system}

	\begin{alertblock}{Underlying Idea\footnotemark}
		\begin{enumerate}
			\item Take a dynamical system with well specified stable behaviour
			\item Add another term that makes it follow some interesting trajectory
		\end{enumerate}
	\end{alertblock}

	\vskip 1em			
	There are two kinds of DMP:
	\vskip -0.5em
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{center}
				\textsc{Discrete} DMP
				\vskip -0.5em
				\begin{figure}
					\includegraphics[height=2cm]{images/ptp_motion}
					\vskip -0.5em
					\caption{Point to Point Motion}
				\end{figure}
			\end{center}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{center}
				\textsc{Rhythmic} DMP
				\vskip -0.5em
				\begin{figure}
					\includegraphics[height=2cm]{images/human_locomotion}
					\vskip -0.5em
					\caption{Human Walking}
				\end{figure}
			\end{center}
		\end{column}
	\end{columns}

	\footnotetext{\tiny Ijspeert, A. J., J. Nakanishi, and S. Schaal. ``Learning control policies for movement imitation and movement recognition." Neural information processing system. Vol. 15. 2003.}
\end{frame}

\begin{frame}[noframenumbering]{Formulation of DMP}
	Let's start with point attractor dynamics\footnote{\tiny Ijspeert, Auke Jan, Jun Nakanishi, and Stefan Schaal. ``Movement imitation with nonlinear dynamical systems in humanoid robots." Robotics and Automation, 2002. Proceedings. ICRA'02. IEEE International Conference on. Vol. 2. IEEE, 2002.}

	\vskip -1em
	\begin{equation}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y})
		\label{eq:attractor}
	\end{equation}
	\vskip -0.5em
	where:
	\begin{itemize}
		\item $y$ is system state and $g$ is goal state
		\item $\alpha$ and $\beta$ are gain terms
	\end{itemize}

	\vskip 1em
	Now add a forcing term $f$ on eq(\ref{eq:attractor}) that will let us to modify this trajectory
	\begin{equation}
		\ddot{y} = \alpha_y ( \beta_y (g - y) - \dot{y}) + f
		\label{eq:attractor_with_f}
	\end{equation}
	$f$ is nonlinear function defined over time.

	\begin{exampleblock}{}
		\begin{itemize}
			\item[*] The introduced system in eq(\ref{eq:attractor_with_f}) is called the \textit{canonical system}.
			\item[*]  It is denoted by $x$ as $\dot{x} = -\alpha_x x$
		\end{itemize}
	\end{exampleblock}
\end{frame}

\begin{frame}[noframenumbering]{Formulation of DMP}
	The forcing function $f$ is defined as a function of the canonical system:
	\begin{equation}
		f(x,g) = \frac{\Sigma_{i=1}^N \psi_i w_i}{\Sigma_{i=1}^N \psi_i} x(g - y_0)
		\label{eq:cs_with_f}
	\end{equation}
	\vskip -1.0em
	where:
	\begin{itemize}
		\item $y_0$ is the initial state of the system
		\item $w_i$ is a weighting for a given basis function $\psi_i$
		\item $\psi_i = \textrm{exp}\left( -h_i \left( x - c_i\right)^2 \right)$ is Gaussian with mean $c_i$ and variance $h_i$
	\end{itemize}
	\begin{alertblock}{}
		\small Forcing function $f$ is a set of Gaussians that are \textit{activated} as the canonical system $x$ converges to its target.
	\end{alertblock}

	\vskip -0.5em
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2cm]{images/psi_activation}
				\vskip -0.5em
				\caption{$\psi$ Activation}
			\end{figure}
		\end{column}

		\begin{column}{0.5\textwidth}
			\begin{figure}
				\includegraphics[height=2cm]{images/weighted_summation}
				\vskip -0.5em
				\caption{Weighted Summation}
			\end{figure}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[noframenumbering]{Imitating a desired path}
	\linespread{1.4}
	The forcing term $f$ which affects the system acceleration, can be re-written as
	\begin{equation}
		\textbf{f}_d = \ddot{\textbf{y}}_d - \alpha_y ( \beta_y (g - \textbf{y}) - \dot{\textbf{y}})
		\label{eq:imitate_f}
	\end{equation}
	where
	\begin{itemize}
		\item $\textbf{y}_d$ is desired trajectory, given by $\ddot{\textbf{y}}_d = \frac{\partial}{\partial t} \dot{\textbf{y}}_d = \frac{\partial}{\partial t} \frac{\partial}{\partial t} \textbf{y}_d$
	\end{itemize}

	\begin{exampleblock}{Forcing term}					
		\begin{itemize}
			\item Comprised of weighted summation of basis functions
			\item We can use optimization technique like LWR\footnotemark
			      \begin{itemize}
			      	\item[*] To choose the weights over our basis functions
			      	\item[*] Minimize
			      	      \vskip -2em
			      	      \begin{equation}
			      	      	\Sigma_t \psi_i(t)(f_d(t) - w_i (x(t) (g - y_0)))^2
			      	      	\label{eq:minize_fd}
			      	      \end{equation}
			      \end{itemize}
		\end{itemize}
	\end{exampleblock}

	\footnotetext{\tiny Cleveland, William S. ``Robust locally weighted regression and smoothing scatterplots." Journal of the American statistical association 74.368 (1979): 829-836.}
\end{frame}

\begin{frame}[noframenumbering]{Imitating a desired path}
	The solution\footnote{\tiny Schaal, Stefan, Christopher G. Atkeson, and Sethu Vijayakumar. ``Scalable techniques from nonparametric statistics for real time robot learning." Applied Intelligence 17.1 (2002): 49-60.} of eq(\ref{eq:minize_fd}) $w_i = \frac{\textbf{s}^T \pmb{\psi}_i \textbf{f}_d}{\textbf{s}^T \pmb{\psi}_i \textbf{s}}$	\\
	where
	\begin{itemize}
		\item[] $\textbf{s} = \left( \begin{array}{c}x_{t_0}(g - y_0) \\ \vdots \\ x_{t_N}(g - y_0) \end{array} \right)$ and $\pmb{\psi}_i = \left( \begin{array}{ccc} \psi_i(t_0) & \dots & 0 \\ 0 & \ddots & 0 \\ 0 & \dots & \psi_i(t_n) \end{array} \right)$
	\end{itemize}

	\begin{figure}
		\includegraphics[width=0.9\textwidth]{images/imitate_path}
	\end{figure}
	\vskip-0.7em
	%\centering{
	\tiny{Back to \hyperlink{main}{\beamerbutton{main}}}
	%}
\end{frame}
\end{document}
